

\documentclass[ProjectPlan_innit.tex]{subfiles}
\begin{document}

\renewcommand\refname{VI. Initial Literature List}
\begin{thebibliography}{1}


\subsection{Changing to Agile}
\bibitem{}
Boehm, B, and Richard T. \emph{"Management challenges to implementing agile processes in traditional development organizations."}Software, ieee 22.5 (2005): 30-39.

\bibitem{}
Duka, Denis. \emph{"Adoption of agile methodology in software development."} Information \& Communication Technology Electronics \& Microelectronics (MIPRO), 2013 36th International Convention on. IEEE, 2013.


\subsection{Continuous Integration}
\bibitem{} 
Rogers, R. O. \emph{"Scaling continuous integration."} Extreme Programming and Agile Processes in Software Engineering. Springer Berlin Heidelberg, 2004. 68-76.
\bibitem{} 
F.A.~Abdul, and M.C.F.~Fhang. \emph{"Implementing continuous integration towards rapid application development."} Innovation Management and Technology Research (ICIMTR), 2012 International Conference on. IEEE, pp. 118-123, 2012.
\bibitem{} 
Stolberg, Sean. \emph{"Enabling agile testing through continuous integration."} Agile Conference, 2009. AGILE'09.. IEEE, 2009.
\bibitem{}
Neely, Steve, and Steve Stolt. \emph{"Continuous Delivery? Easy! Just Change Everything (well, maybe it is not that easy)."} Agile Conference (AGILE), 2013. IEEE, 2013.
\bibitem{} 
Rehn, Christian. \emph{"Continuous Integration: Aspects in Automation and Configuration Management."} (2012).
\bibitem{} 
Pulkkinen, Ville. \emph{"Continuous Deployment of Software."} Cloud-Based Software Engineering (2013): 46.


\subsection{Model Driven Development}
\bibitem{} 
MacDonald, Anthony, Danny Russell, and Brenton Atchison. \emph{"Model-driven development within a legacy system: an industry experience report."} Software Engineering Conference, 2005. Proceedings. 2005 Australian. IEEE, 2005.

\bibitem{}
Brown, Alan W., Sridhar Iyengar, and Simon Johnston. \emph{"A Rational approach to model-driven development."} IBM Systems Journal 45.3 (2006): 463-480.

\subsection{One Track}
\bibitem{} 
L.~Hribar, S. ~Sapunar and A.~Burilović, \emph{"First Time Right in AXE using One track and Stream Line Development"} Proceedings MIPRO, 2008.

\subsection{Feature Toggles}
\bibitem{} 
Rehn, Christian. \emph{"Continuous Integration: Aspects in Automation and Configuration Management."} (2012).
\bibitem{}
Hüttermann, Michael. \emph{"Building Blocks of DevOps."} DevOps for Developers. Apress, 2012. 33-47.


\subsection{Cross-Functional}
\bibitem{} 
S.~Ghobadi, \emph{Challenges of cross-functional software development teams: A conceptual study }, Journal of Information Technology Management 22.3, 2011
\bibitem{} 
Marchwinski, Theresa, and Karen Mandziuk. \emph{"The technical communicator’s role in initiating cross-functional teams."} Technical Communication 47.1 (2000): 67-76.

\subsection{Lean}
\bibitem{} 
Poppendieck, M., and M. A. Cusumano. \emph{"Lean software development: A tutorial."} Software, IEEE 29.5 (2012): pp.26-32.


\subsection{Knowledge Sharing}
\bibitem{} 
Chau, T., and F. Maurer. \emph{"Knowledge sharing in agile software teams."} Logic versus approximation. Springer Berlin Heidelberg, 2004. pp.173-183.

\subsection{Large-scale software development}
\bibitem{} 
Bjarnason, E., K. Wnuk, and B. Regnell. \emph{"Are you biting off more than you can chew? A case study on causes and effects of overscoping in large-scale software engineering."} Information and Software Technology 54.10, 2012: pp.1107-1124.


\subsection{Agile MDD}
\bibitem{}
Stojanovic, Z., A. Dahanayake, and H. Sol. \emph{"Component-oriented agile software development."}, Extreme Programming and Agile Processes in Software Engineering. Springer Berlin Heidelberg, 2003. pp.315-318.

\bibitem{}
Zhang, Y., and S. Patel. \emph{"Agile model-driven development in practice."} IEEE software 28.2, 2011: 84-91.

\bibitem{}
Ambler, Scott W. \emph{"Agile model driven development is good enough."} Software, IEEE 20.5, 2003: pp.71-73.



\subsection{Unit Testing}
\bibitem{} 
G.~Engels, M. ~Lohmann and B.~Güldali, \emph{Towards model-driven unit testing}, Springer Berlin Heidelberg: In Models in Software Engineering, 2007, pp.182-192.


\end{thebibliography}


\end{document}