\documentclass[final_report_innit.tex]{subfiles}
\begin{document}
\appendix
\section{Appendix A}

\subsection{Questionnaire}

\begin{enumerate}
	\item General questions
	\begin{enumerate}
		\item What is your position? (E.g. developer, tester, manager).
		\item Do you work in a ``manual coding'' team or in a MDSD team?
	\end{enumerate}
	\item Continuous Integration
	\begin{enumerate}
		\item How has the introduction of Continuous Integration affected your ability to meet deadlines and deliver on time?
		\item How do you percieve that Continuous Integration has affected the quality of what You deliver?
		\item How do you percieve that Continuous Integration has helped you find your role in the group?
		\item How time consuming has it been for you to adapt to Continuous Integration in your daily work?
	\end{enumerate}
	\item Cross-functional Teams
	\begin{enumerate}
		\item How has the introduction of Cross-functional Teams affected your ability to meet deadlines and deliver on time?
		\item How do you percieve that Cross-functional Teams has affected the quality of what You deliver?
		\item How do you percieve that Cross-functional Teams has helped you find your role in the group?
		\item How time consuming has it been for you to adapt to Cross-functional Teams in your daily work?
	\end{enumerate}
	\item Feature Toggles \& One Track
	\begin{enumerate}
		\item How has the introduciton of Feature Toggles \& One Track affected your ability to meet deadlines and deliver on time?
		\item How do you percieve that Feature Toggles \& One Track has affected the quality of what You deliver?
		\item How do you percieve that Feature Toggles \& One Track has helped you find your role in the group?
		\item How time consuming has it been for you to adapt to Feature Toggles \& One Track Teams in your daily work?
	\end{enumerate}
	\item Unit Testing
	\begin{enumerate}
		\item How has the introduction of Unit Testing affected your ability to meet deadlines and deliver on time?
		\item How do you percieve that Unit Testing has affected the quality of what You deliver?
		\item How do you percieve that Unit Testing has helped you find your role in the group?
		\item How time consuming has it been for you to adapt to the increased Unit Testing in your daily work?
	\end{enumerate}
	\item Component Testing
	\begin{enumerate}
		\item How has the introduction of Component Testing affected your ability to meet deadlines and deliver on time?
		\item How do you percieve that Component Testing has affected the quality of what You deliver?
		\item How do you percieve that Component Testing has helped you find your role in the group?
		\item How time consuming has it been for you to adapt to the increased Component Testing in your daily work?
	\end{enumerate}
\end{enumerate}

\subsection{Interview questions}

\begin{enumerate}
	\item General MDSD questions
	\begin{enumerate}
		\item Is there any official/proper word for ``manual coding'' in the context of manual coding vs MDSD?
		\item What ``is'' MDSD? (Programming paradigm, development method, toolchain).
		\item What is the distribution between non-MDSD and MDSD?
		\item On what basis are teams/subsystems selected to change to MDSD?
		\item Why did you change to MDSD?
		\item What have been the struggles with MDSD?
		\item What are the positive sides of MDSD?
		\item Were any other development methods than MDSD considered?
		\item Do you think that CI / OT / CFT / UT / CT was implemented as one ``package''?
		\item Were any of the changes bottom-up?
	\end{enumerate}
	\item Change Management theories
	\begin{enumerate}
		\item Motors \& Presc/Constr \& Delib/Emergent
		\begin{enumerate}
			\item Have the changes in Ericsson had a clear plan? 
			\item Do you perceive that the changes had a clear plan/goal? 
		\end{enumerate}
		\item Driving/Restricting forces
		\begin{enumerate}
			\item What is the largest obstacle for change at Ericsson?
			\item What has been the main driving force for previous changes at Ericsson?
		\end{enumerate}
		\item Lewin group stuff
		\begin{enumerate}
			\item Are the changes targeted towards individuals or teams?
		\end{enumerate}
	\end{enumerate}
	\item Results Analysis
	\begin{enumerate}
		\item MDSD developers seem to prefer One Track and FT a lot more than manual coders do. 
		\item Manual coders seem to prefer unit testing a lot more than MDSD developers do.
		\item Manual coders seem to prefer cross functional teams slightly more than MDSD developers do.
		\item Results related to cross functional teams were the most positive. 
		\item Component testing was equivalent for both groups while the MDSD group seemed to rate unit testing with a lower score.
	\end{enumerate}
\end{enumerate}

\subsection{Questionnaire Responses}
Tables showing collected responses. 1 through 5 correlates to alternatives [[DO WE HAVE TO LIST ALL DIFFERENT SCALES?!?!?!?! ]]. \textit{FALSE} indicates ``not applicable'', ``did not answer''.

\rowcolors{1}{greyOdd}{greyEven}
\begin{center}
% Manual coding responses
\begin{tabular}[b]{l | c | c | c | c | c | c | c | c}
	& \textbf{MC1} & \textbf{MC2} & \textbf{MC3} & \textbf{MC4} & \textbf{MC5} & \textbf{MC6} & \textbf{MC7} & \textbf{MC8} \\ %\hline
	\textbf{CI-P} & 4 & 5 & 4 & 4 & 4 & \textit{FALSE} & 3 & 5 \\ %\hline
	\textbf{CI-Q} & 3 & 4 & 3 & 3 & 4 & \textit{FALSE} & 3 & 5 \\ %\hline
	\textbf{CI-PF} & 3 & 3 & 3 & 3 & 4 & \textit{FALSE} & 3 & 5 \\ %\hline
	\textbf{CI-EOI} & 5 & 4 & 4 & 5 & 4 & \textit{FALSE} & 3 & 5 \\ %\hline
	\textbf{CF-P} & 4 & 5 & 4 & 4 & \textit{FALSE} & \textit{FALSE} & 4 & 5 \\ %\hline
	\textbf{CF-Q} & 4 & 5 & 2 & 4 & \textit{FALSE} & \textit{FALSE} & 4 & 5 \\ %\hline
	\textbf{CF-PF} & 3 & 3 & 3 & 3 & \textit{FALSE} & \textit{FALSE} & 5 & 5 \\ %\hline
	\textbf{CF-EOI} & 4 & 5 & 4 & 5 & \textit{FALSE} & \textit{FALSE} & 4 & 5 \\ %\hline
	\textbf{FD-P} & 5 & \textit{FALSE} & 4 & \textit{FALSE} & 3 & \textit{FALSE} & 2 & 2 \\ %\hline
	\textbf{FD-Q} & 4 & \textit{FALSE} & 3 & \textit{FALSE} & 3 & \textit{FALSE} & 3 & 3 \\ %\hline
	\textbf{FD-PF} & 3 & \textit{FALSE} & 3 & \textit{FALSE} & 3 & \textit{FALSE} & 3 & 3 \\ %\hline
	\textbf{FD-EOI} & 1 & \textit{FALSE} & 4 & \textit{FALSE} & 2 & \textit{FALSE} & 3 & 1 \\ %\hline
	\textbf{UT-P} & 2 & 3 & 5 & 5 & 3 & \textit{FALSE} & \textit{FALSE} & 3 \\ %\hline
	\textbf{UT-Q} & 4 & 3 & 5 & 5 & 4 & \textit{FALSE} & \textit{FALSE} & 3 \\ %\hline
	\textbf{UT-PF} & 3 & 3 & 3 & 3 & 3 & \textit{FALSE} & \textit{FALSE} & 5 \\ %\hline
	\textbf{UT-EOI} & 5 & 2 & 2 & 4 & 3 & \textit{FALSE} & \textit{FALSE} & 5 \\ %\hline
	\textbf{CT-P} & 2 & \textit{FALSE} & 5 & 4 & \textit{FALSE} & \textit{FALSE} & \textit{FALSE} & \textit{FALSE} \\ %\hline
	\textbf{CT-Q} & 4 & \textit{FALSE} & 5 & 5 & \textit{FALSE} & \textit{FALSE} & \textit{FALSE} & \textit{FALSE} \\ %\hline
	\textbf{CT-PF} & 3 & \textit{FALSE} & 3 & 3 & \textit{FALSE} & \textit{FALSE} & \textit{FALSE} & \textit{FALSE} \\ %\hline
	\textbf{CT-EOI} & 4 & \textit{FALSE} & 1 & 5 & \textit{FALSE} & \textit{FALSE} & \textit{FALSE} & \textit{FALSE} \\ %\hline
	\multicolumn{9}{c}{\cellcolor{white} \textbf{Manual coding responses}} \\
\end{tabular}

%MDSD responses
\begin{tabular}[b]{l | c | c | c | c | c | c}
	& \textbf{MDSD1} & \textbf{MDSD2} & \textbf{MDSD3} & \textbf{MDSD4} & \textbf{MDSD5} & \textbf{MDSD6} \\ %\hline
	\textbf{CI-P} & 4 & 4 & 4 & 4 & \textit{FALSE} & \textit{FALSE} \\ %\hline
	\textbf{CI-Q} & 4 & 4 & 4 & 4 & \textit{FALSE} & \textit{FALSE} \\ %\hline
	\textbf{CI-PF} & 3 & 3 & 3 & 3 & \textit{FALSE} & \textit{FALSE} \\ %\hline
	\textbf{CI-EOI} & 4 & 5 & 4 & 5 & \textit{FALSE} & \textit{FALSE} \\ %\hline
	\textbf{CF-P} & \textit{FALSE} & 4 & 4 & \textit{FALSE} & \textit{FALSE} & \textit{FALSE} \\ %\hline
	\textbf{CF-Q} & \textit{FALSE} & 1 & \textit{FALSE} & \textit{FALSE} & \textit{FALSE} & \textit{FALSE} \\ %\hline
	\textbf{CF-PF} & \textit{FALSE} & 3 & 3 & \textit{FALSE} & \textit{FALSE} & \textit{FALSE} \\ %\hline
	\textbf{CF-EOI} & \textit{FALSE} & 5 & 5 & \textit{FALSE} & \textit{FALSE} & \textit{FALSE} \\ %\hline
	\textbf{FD-P} & 4 & 4 & 4 & 4 & \textit{FALSE} & \textit{FALSE} \\ %\hline
	\textbf{FD-Q} & 4 & 5 & 5 & 4 & \textit{FALSE} & \textit{FALSE} \\ %\hline
	\textbf{FD-PF} & 3 & \textit{FALSE} & \textit{FALSE} & 3 & \textit{FALSE} & \textit{FALSE} \\ %\hline
	\textbf{FD-EOI} & 4 & 4 & 5 & 5 & \textit{FALSE} & \textit{FALSE} \\ %\hline
	\textbf{UT-P} & 3 & \textit{FALSE} & \textit{FALSE} & 3 & \textit{FALSE} & \textit{FALSE} \\ %\hline
	\textbf{UT-Q} & 3 & \textit{FALSE} & \textit{FALSE} & 3 & \textit{FALSE} & \textit{FALSE} \\ %\hline
	\textbf{UT-PF} & 3 & \textit{FALSE} & \textit{FALSE} & 3 & \textit{FALSE} & \textit{FALSE} \\ %\hline
	\textbf{UT-EOI} & 2 & 1 & \textit{FALSE} & 2 & \textit{FALSE} & \textit{FALSE} \\ %\hline
	\textbf{CT-P} & 4 & \textit{FALSE} & \textit{FALSE} & 4 & \textit{FALSE} & \textit{FALSE} \\ %\hline
	\textbf{CT-Q} & 5 & \textit{FALSE} & \textit{FALSE} & 5 & \textit{FALSE} & \textit{FALSE} \\ %\hline
	\textbf{CT-PF} & 3 & \textit{FALSE} & \textit{FALSE} & 3 & \textit{FALSE} & \textit{FALSE} \\ %\hline
	\textbf{CT-EOI} & 4 & 1 & 1 & 4 & \textit{FALSE} & \textit{FALSE} \\ %\hline
	\multicolumn{7}{c}{\cellcolor{white} \textbf{MDSD responses}} \\
\end{tabular}
\end{center}
\end{document}